The necessity of hypermedia RDF and an approach to achieve it

### 2012-04-12 eswc-2012/workshop2.tex
-the
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@225 43ef1190-90fd-4dd7-a769-d0121f02b80e

In the \cite{linkeddataissue} Tim Berners-Lee
notes ``To make the data be effectively linked, someone who only has
the URI of something must be able to find their way the SPARQL
endpoint.'', but this is generally not possible today without
requiring out-of-band information.

>>>>

In \cite{linkeddataissue} Tim Berners-Lee notes ``To make the data be
effectively linked, someone who only has the URI of something must be
able to find their way the SPARQL endpoint.'', but this is generally
not possible today without requiring out-of-band information.
